---
title: "assignment b-1"
author: "Jeenat Mehareen"
date: "2024-10-31"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
suppressPackageStartupMessages(library(devtools)) # for devtools package
suppressPackageStartupMessages(library(dplyr)) # for data maniupulation
suppressPackageStartupMessages(library(testthat)) # for testing functions
suppressPackageStartupMessages(library(digest)) #digests outputs for testing 
suppressPackageStartupMessages(library(palmerpenguins)) # for testing a sample tibble

```


**Exercise 1 and 2: Making and documenting my function**
```{r}
#' Convert Millimeters to Inches
#'
#' This function converts measurements from millimeters (mm) to inches: 1 inch = 25.4 mm.
#' It is designed to ignore non-numeric inputs.
#' It will accept a numeric vector as input and return vecotr of converted values
#' 
#' 
#' @param mm A numeric vector, measurements are in milimeters, hence the name mm. Non-numeric values will result in an error.
#' @return A numeric vector,it will convert mm to inches. If input values are NA it will return "NA"
#' @export
#'
#' @examples Showing some example for usage of single value, vectors and NA 
#' mm_to_in(25.4) # Should return 1
#' mm_to_in(c(25.4, 127)) # Should return 1 and 5
#' mm_to_in(NA) # Should return NA


mm_to_in <- function(mm) {
  # Check if the input is numeric; throw an error if not
  if (!is.numeric(mm)) {
    stop("Input must be a numeric vector, measurements must be in mm")
  }
  
  # otherwise convert the value
  inch <- mm / 25.4
  return(inch)
}
```

**Exercise 3: Examples**

<p> The following demonstrates an example unit conversion using manual input of 200mm <p>
```{r}
mm_to_in(200)
```

<p> This shows an example using a unit conversion on a column in a dataframe (using penguins and flipper_length_mm) <p>

```{r}
a <- penguins %>%
  mutate(mm_to_in(flipper_length_mm))
a
```
<p> This shows error when trying to convert string values with the function <p>

<p> This shows an error with the message "Input must be a numeric vector, measurements must be in mm" when trying to convert string values with the function: </p>


```{r, error = TRUE}
# Attempting to convert non-numeric input should result in an error
mm_to_in("fail") # This will trigger an error since the input is not numeric
```

**Exercise 4: Testing the function**




```{r}
##Test 1
test_that("Testing mm_to_in function",{
   expect_equal(mm_to_in(124), 124 / 25.4)
             
})
```

```{r}
##Test 2
test_that("Testing mm_to_in function",{
expect_equal(mm_to_in(c(25.4, NA)), c(25.4 / 25.4, NA))
})
```

```{r}
##Test 3
test_that("Testing mm_to_in function",{
  expect_error(mm_to_in("stat"), "Input must be a numeric vector")
})
```


